\begin{thm}
    Let $0\to U \xto{\alpha} V \xto{\beta} W \to 0$ be a SES of $R$-modules and $D$ be any $R$-module. Then we have a LES 
    \[0 \to \h_R(D,U) \to \h_R(D,V)\to \h_R(D,W)\]
    \[\to \ext_R^1 (D,U)\to \ext_R^1(D,V)\to \ext_R^1(D,W)\to \ext_R^2(D,U)\to \dots\]
\end{thm}
\begin{proof}
    Take a projective resolution $P_\bullet \twoheadrightarrow D$ of $D$. Taking $\h_R(-, U), \h_R(-, V)$, and $\h_R(-, W)$ we obtain
    \[\begin{tikzcd}[sep=small]
	&& 0 && 0 && 0 \\
	\\
	0 && {\h_R(P_0, U)} && {\h_R(P_1, U)} && {\h_R(P_2, U)} && \dots \\
	\\
	0 && {\h_R(P_0, V)} && {\h_R(P_1, V)} && {\h_R(P_2, V)} && \dots \\
	\\
	0 && {\h_R(P_0, W)} && {\h_R(P_1, W)} && {\h_R(P_2, W)} && \dots \\
	\\
	&& 0 && 0 && 0
	\arrow[from=1-3, to=3-3]
	\arrow[from=1-5, to=3-5]
	\arrow[from=1-7, to=3-7]
	\arrow[from=3-1, to=3-3]
	\arrow["{d_1^*}", from=3-3, to=3-5]
	\arrow["{\alpha_*}", from=3-3, to=5-3]
	\arrow["{d_2^*}", from=3-5, to=3-7]
	\arrow["{\alpha_*}", from=3-5, to=5-5]
	\arrow["{d_3^*}", from=3-7, to=3-9]
	\arrow["{\alpha_*}", from=3-7, to=5-7]
	\arrow[from=5-1, to=5-3]
	\arrow["{d_1^*}", from=5-3, to=5-5]
	\arrow["{\beta_*}", from=5-3, to=7-3]
	\arrow["{d_2^*}", from=5-5, to=5-7]
	\arrow["{\beta_*}", from=5-5, to=7-5]
	\arrow["{d_3^*}", from=5-7, to=5-9]
	\arrow["{\beta_*}", from=5-7, to=7-7]
	\arrow[from=7-1, to=7-3]
	\arrow["{d_1^*}", from=7-3, to=7-5]
	\arrow[from=7-3, to=9-3]
	\arrow["{d_2^*}", from=7-5, to=7-7]
	\arrow[from=7-5, to=9-5]
	\arrow["{d_3^*}", from=7-7, to=7-9]
	\arrow[from=7-7, to=9-7]
    \end{tikzcd}\]
    where the columns are exact, since $P_0$ is projective. This implies that we get a SES of complexes
    \[0 \to \h_R(P_\bullet, U) \to \h_R(P_\bullet, V)\to \h_R(P_\bullet, W)\to 0\]
    We shall denote this SES as $0 \to X_\bullet \to Y_\bullet \to Z_\bullet \to 0$. This induces a LES on the cohomology, i.e.
    \[0 \to H^1(X_\bullet) \to H^1(Y_\bullet) \to H^1(Z_\bullet) \to H^2(X_\bullet) \to H^2(Y_\bullet) \to H^2(Z_\bullet) \to \dots\]
    where each cohomology represents their respective Ext groups on either $U,V,$ or $W$. Recall also that the $0$-th Ext group is isomorphic to the hom set. Thus rewriting the above LES gives us
    \[0 \to \h_R(D,U) \to \h_R(D,V)\to \h_R(D,W)\]
    \[\to \ext_R^1 (D,U)\to \ext_R^1(D,V)\to \ext_R^1(D,W)\to \ext_R^2(D,U)\to \dots\]
    as required.
\end{proof}

\begin{re}
    Similarly, note that since $\h_R(X,D)\cong \ext_R^0(X,D)$, thus the whole LES above is a LES of $\ext$ groups.
\end{re}

\medskip

\begin{re}
    Since $\h_R(D,-)$ is a left exact covariant functor, we obtained a right covariant derived functor $\ext_R^m(D,-):\text{R-mod} \to \text{Ab}$. This is 'dual' to the relation between $\h_R(-,D)$ and $\ext_R^n(-,D)$.
\end{re}

\medskip

\begin{thm}
    Let $P$ be an $R$-module. TFAE:
    \begin{enumerate}
        \item $P$ is projective.
        \item $\ext_R^1(P,B)=0$ for all $R$-module $B$.
        \item $\ext_R^n(P,B)=0$ for all $n\geq 1$ and $R$-module $B$.
    \end{enumerate}
\end{thm}
\begin{proof}
    The proof is left as a tutorial question.
\end{proof}

\begin{ex}
    \hfill
    
    \begin{enumerate}
        \item For any free $R$-module $F$, we have $\ext_R^n(F,B)=0$ for any $n\geq 1$ and $R$-module $B$. In particular $\ext_\Z^n(\Z^m,B)=0$ for all $n\geq 1$ and $m\geq 1$.
        \item We compute $\ext_\Z^n(A,B)$ when $A$ is finitely generated $\Z$-module. Since $\Z$ is a PID, by the classification of finitely generated module over PID, we have 
        \[A\cong \Z^m \oplus (\Z/d_1\Z) \oplus \dots \oplus (\Z/d_\ell \Z) \]
        where $d_i\neq 0 $ for all $i$. In tutorial we will prove that
        \[\ext_R^n\br{\bigoplus V_i}, W\cong \prod \ext_R^n(V_i, W)\]
        But we have only finite number of items (since finitely generated), so 
        \[\ext_\Z^n(A,B)\cong \br{\bigoplus_{i=1}^m \ext_\Z^n(\Z,B)} \oplus \br{\bigoplus_{i=1}^\ell\ext_\Z^n(\Z/d_i\Z, B)}\]
    \end{enumerate}
    So when $n=0$ we have
    \[\ext_\Z^0(A,B) \cong \br{\bigoplus_{i=1}^m \h_\Z(\Z,B)} \oplus \br{\bigoplus_{i=1}^\ell\h_\Z(\Z/d_i\Z, B)}\cong B^m \oplus  \bigoplus_{i=1}^\ell\ _{d_i}B\]
    where $_{d_i}B:= \sbr{b\in B : d_i b = 0}$.

    When $n=1$ we have
    \[\ext_\Z^1(A,B) \cong 0 \oplus \bigoplus_{i=1}^\ell \ext_\Z^1 (\Z/d_i\Z, B) = \bigoplus B/d_i B\]
    When $n\geq 2$ we have 
    \[\ext_\Z^n(A,B)\cong 0 \oplus \bigoplus_{i=1}^\ell \ext_\Z^n(\Z/d_i\Z, B) = 0\]
\end{ex}

\medskip

\begin{defn} [Injective resolution]
    An injective resolution of an $R$-module $W$ is an exact sequence 
    \[0 \to W \to Q_0 \to Q_1 \to \dots\]
    such that each $Q_i$ is injective $R$-module. We denote the injective resolution of $W$ as $W \hookrightarrow Q_\bullet$.
\end{defn}

\medskip

\begin{pro}
    Every $R$-module has an injective resolution.
\end{pro}
\begin{proof}
    
    The whole proof is similar to the proof of existence of projective resolution, except that we will be taking the cokernel.

    Recall that every $R$-module is a submodule of some injective $R$-module. Thus, suppose given $W$ is an $R$-module, let $Q_0$ be an injective $R$-module such that $W\subseteq Q_0$. We have 
    \[0\to W \xto\iota Q_0\]
    Next we need to construct $Q_1$ from the existing information. Consider $\coker \iota$, i.e. $Q_0/\im\iota$, we have that $\pi_0: Q_0\twoheadrightarrow \coker \iota$ is the canonical surjection. Note $\coker \iota$ is also an $R$-module, thus it is contained in some injective $R$-module, say $Q_1$. Therefore, we can simply take the composition map of $Q_0$ to $\coker \iota$ and $\coker \iota$ to $Q_1$, giving us:
    \[\begin{tikzcd}[sep=small]
	0 && W && {Q_0} && {Q_1} \\
	\\
	&&&&& {\coker \iota = Q_0/\im \iota}
	\arrow[from=1-1, to=1-3]
	\arrow[from=1-3, to=1-5]
	\arrow["d_1",dashed, from=1-5, to=1-7]
	\arrow["\pi_0"',two heads,from=1-5, to=3-6]
	\arrow[hook, from=3-6, to=1-7]
    \end{tikzcd}\]
    Note that since the map from $\coker \iota$ to $Q_1$ is injective, thus $\ker d_1 = \ker \pi_0$, and it is clear that $\ker \pi_0=\im \iota$. This shows that $\ker d_1 = \im \iota$, implying that we have exactness. Repeat the above procedure again we obtain:
    \[\begin{tikzcd}[sep=small]
	0 && W && {Q_0} && {Q_1} && {Q_2} \\
	\\
	&&&&&&& {\coker d_1= Q_1/\im d_1}
	\arrow[from=1-1, to=1-3]
	\arrow[from=1-3, to=1-5]
	\arrow["{d_1}", from=1-5, to=1-7]
	\arrow["{d_2}", dashed, from=1-7, to=1-9]
	\arrow[two heads, from=1-7, to=3-8]
	\arrow[hook, from=3-8, to=1-9]
    \end{tikzcd}\]
    and the exactness can be verfied similarly. Inductively we can construct an exact sequence of injective modules, thus completing the proof.
\end{proof}

\begin{defn} [Alternative definition of $\ext$]
    Take an injective resolution $W\hookrightarrow Q_\bullet$ of $W$ and take $\h_R(V,-)$. which we get 
    \[0 \xto{d_0^*} \h_R(V,Q_0) \xto{d_0^*} \h_R(V,Q_0) \xto{d_0^*} \h_R(V,Q_0) \to \dots \]
    The $n$-th cohomology group of this complex is defined as 
    \[\ext_R^n(V,W) := \frac{\ker d_{n+1}^*}{\im d_n^*}\]

\end{defn}

\medskip

\begin{re}
    Despite we are unable to prove that, but we have the following fact: the Ext group constructed from injective resolution is independent of the choice of the starting injective resolution. Also, the Ext group constructed from injective resolution is isomorphic to if it is constructed from a projective resolution.
\end{re}

\medskip

\begin{ex}
    We verify that the $\ext^0_R(V,W)$ constructed from projective resolution and injective resolution is isomorphic. Starting from $0$-th Ext group constructed from an injective resolution:
    \begin{align*}
        \ext_R^0(V,W) &= \ker d_1^* \\
        &= \sbr{f:V\to Q_0:d_1\circ f = 0}\\
        &= \sbr{f:V\to Q_0:\im f\subseteq \ker d_1}\\
        &= \sbr{f:V\to Q_0 : \im f\subseteq \im \iota, \iota: W\hookrightarrow Q_0}\\
        &= \sbr{f:V\to \iota(W)}\\
        &\cong \h_R(V,W)
    \end{align*}
    We have shown that the $0$-th Ext group constructed from projective resolution is also isomorphic to $\h_R(V,W)$, this shows the $0$-th Ext group is independet of the method of construction.
\end{ex}

\medskip

\begin{re} [Enough projective and enough injective]
    In fact, all the mentioned theory can be generalized to any category.
    
    A category $\mathcal C$ has enough projective if for any object $X$ in $\mathcal C$ there is a projective object $P$ such that $P\to X$ is an epimorphism. Since the definition of projective module is nothing except of lifting of maps, we need not 'module-like' object to define a projective object in the category $\mathcal C$, assuming that we can 'lift' the map.

    Similarly, the category has enough injective if for any object $X$ in $\mathcal C$ there is an injective object $I$ such that $X\to I$ is a monomorphism. Construction of injective object shares the same philosophy, as it just requires construction of maps.

    In the category R-mod, it is nice in the sense that it has both enough projective and enough injective. However, there might be some category where it is only enough projective, or vice versa. In this case, we might be restricted to construct the Ext group only from the projective resolution, or vice versa. The above says that they are equivalent.
\end{re}

\medskip

\begin{ex}
    \hfill

    \begin{enumerate}
        \item Let $A$ and $B$ be abelian groups. We compute $\ext_\Z^n(A,B)$ (again) using the injective resolution of $B$. Let $Q_0$ be an injective $\Z$-module such that $B\subseteq Q_0$. So
        \[0 \to B\to Q_0 \to Q_0/B \to 0\]
        Recall that the quotient of injective module is injective, so $Q_0/B$ is injective, and the above is an injective resolution of $B$. Taking hom we have 
        \[0 \to \h_\Z(A,Q_0) \to \h_\Z(A, Q_0/B) \to 0 \to 0 \to \dots\]
        We see that $\ext_\Z^n(A,B)=0$ for all $n\geq 2$, even without the assumption that $A$ is finitely genererated.
        \item Let $A$ be a torsion abelian group, i.e. any $a\in A$ there exists some $n\neq 0$ such that $n\cdot a = 0$. We compute $\ext_\Z^0(A,\Z) = \h_\Z(A,\Z)$, which we claimed to be $0$, since for any group homomorphism $\varphi:A\to \Z$ and any $a\in A$, let $n\neq 0$ such that $n\cdot a = 0$, and so 
        \[0 = \varphi(0) = \varphi(na) = n\varphi(a)\]
        implying that $\varphi(a)=0$. Since $a$ is arbitrary, so $\varphi$ is the zero map, indicating that $\ext_\Z^0(A,\Z)$ is trivial. Next, we consider $\ext_\Z^1(A,\Z)$. Take 
        \[0 \to \Z \xto{\iota} \Q \xto{\pi} \Q/\Z \to 0\]
        where $\pi$ is the canonical surjection, and $\iota$ is the inclusion map. The above is an injective resolution of $\Z$. Taking hom, we have 
        \[0 \to \h_\Z(A,\Q)\to \h_\Z(A, \Q/\Z) \to 0 \to 0 \to \dots\]
        We claim that $\h_\Z(A,\Q)=0$. To see this, take $\varphi:A\to \Q$ be a group homomorphism and let $a\in A$ and $n\neq 0$ such that $n\cdot a = 0$. Note
        \[0 = \varphi(0) = \varphi(na) = n\varphi(a) \implies \varphi(a)=0\]
        Since $a$ is arbitrary, we have that $\varphi$ is trivial, so $\h_\Z(A,\Q)=0$. As a remark, the first cohomology group is
        \[\ext_\Z^1 (A,\Z) = \h_\Z(A,\Q/\Z)\]
        In literature, the group $\h_\Z(A,\Q/\Z)$ is called the Pontryagin dual group of $A$.
    \end{enumerate}
\end{ex}

\medskip

\begin{re}
    The reason why Ext group has its name is because of the following theorem:

    \medskip

    \begin{thm}
        $\ext^n_R(V,W)$ is the equivalence classes of $n$-fold extensions of exact sequences that takes the following form 
        \[0 \to W \to V_{n-1}\to \dots \to V_0 \to V \to 0\]
    \end{thm}

    When $n=1$, we are considering the equivalence classes of the exact sequences of the form $0\to W \to V_0 \to V \to 0$, which is just SES.

    As an example, take $R=\Z$ and $V=W = \Z/p\Z$. Based on the previous computed example we have that 
    \[\ext_\Z^1(\Z/p\Z, \Z/p\Z) \cong \frac{\Z/p\Z}{p\cdot (\Z/p\Z)} = \Z/p\Z\]
    That is to mean that there are $p$ equivalent classes of SES in the form of 
    \[0 \to \Z/p\Z \to - \to \Z/p\Z \to 0\]
    In particular, they are either equivalent to 
    \[0 \to \Z/p\Z \xto{\iota} (\Z/p\Z)\oplus (\Z/p\Z) \xto{\pi} \Z/p\Z \to 0\]
    or, for any $j=1,2, \dots, p-1$, that 
    \[0 \to \Z/p\Z \to \Z/p^2\Z \xto{\cdot j} \Z/p\Z \to 0\]
    where the formal one splits and the latter one doesn't.
\end{re}

\subsection{Tor group}
\begin{defn} [Tor group]
    Let $D$ be a right $R$-module, $B$ be a left $R$-module and $P_\bullet \twoheadrightarrow B$ be a projective resolution of $B$:
    \[\dots \to P_2\xto{d_2} P_1 \xto{d_1} P_0 \xto{\varepsilon} B \to 0 \to \dots\]
    We then construct the complex by taking tensor product over $R$:
    \[\dots \xto{1\ten d_3} D\ten_R P_2 \xto{1\ten d_2} D\ten_R P_1 \xto{1\ten d_1} D\ten_R P_0 \to 0\]
    which is indeed a complex since $(1\ten d_n)\circ (1\ten d_{n+1}) = 1\ten (d_n\circ d_{n+1}) = 0$, but it is not exact. In fact $D\ten_R -$ is a right exact functor. The $n$-th Tor group is defined to be the $n$-th homology group of this complex, i.e.
    \[\tor_n^R(D,B) := \frac{\ker \br{1\ten d_n}}{\im \br{1\ten d_{n+1}}}\]
    The functor $\tor_n^R(D, -)$ is the left covariant derived functor of the right covariant functor $D\ten_R -$.
\end{defn}

\medskip

\begin{pro}
    $\tor_0^R(D,B)\cong D\ten_R B$.
\end{pro}
\begin{proof}
    By definition, we have that 
    \[\tor_0^R(D,B) = \ker (1\ten d_0) / \im (1\ten d_1)\]
    A direct observation says that $\ker (1\ten d_0)$ is $D\ten_R P_0$.

    Next, note that we have the following exact sequence:
    \[P_1 \xto{d_1} P_0 \xto{\ep} B \to 0\]
    which induces an exact sequence
    \[D\ten_R P_1 \xto{1\ten d_1} D\ten_R P_0 \xto{1\ten \ep} D\ten_R B \to 0\]
    Thus $\im(1\ten d_1) = \ker (1\ten \ep)$. Altogether, we see that 
    \[\tor_{0}^R(D,B) = \frac{D\ten P_0}{\im (1\ten d_1)} = \frac{D\ten P_0}{\ker(1\ten \ep)}\]
    By 1st Isomorphism Theorem, the RHS is isomorphic to $\im(1\ten \ep)$, which is $D\ten_R B$. This completes the proof.
\end{proof}

\begin{ex}
    We compute $\tor_n^\Z(D,\Z/m\Z)$. Let $B= \Z/m\Z$. Consider the projective resolution of $B$:
    \[0 \to \Z \xto{\cdot m} \Z \xto{\bmod m} \Z/m\Z\to 0\]
    Note if $m=0$ we have 
    \[0 \to \Z \xto{\cdot 1} \Z \to 0\]
    In case of $m\neq 0$, remove the term $\Z/m\Z$, and take tensor product. Also, in case of $m=0$, simply take tensor product, 
    \[\dots \to 0 \to D\ten_\Z \Z \xto{(\cdot m)_*} D\ten_\Z \Z \to 0\]
    which is equivalent to that 
    \[\dots \to 0 \to D \xto{\cdot m} D \to 0\]
    Thus we have $\tor_0^\Z(0,\Z/m\Z) = D\ten_\Z \Z/m\Z \cong D/mD$
    where the last equality is a tutorial question. Also
    \[\tor_1^\Z(D,\Z/m\Z) = \ker(\cdot m)/0 =\ _mD = \sbr{d\in D:md=0}\]
\end{ex}

\medskip

\begin{pro}
    \hfill

    \begin{enumerate}
        \item $\tor_n^R(D,B)$ is independent of the choice of the projective resolution of $B$.
        \item For any $f:B\to B'$, we have an induced map of group homomorphism $f_*:\tor_n^R(D,B) \to \tor_n^R(D,B')$.
    \end{enumerate}
\end{pro}

\begin{proof}
    The first statement is left as an tutorial question.

    For the second statement, let $P_\bullet \twoheadrightarrow B$ and $P'_\bullet \twoheadrightarrow B'$ be projective resolutions of $B$ and $B'$ respectively. Then, by Comparison Theorem, we have
    \[\begin{tikzcd}[sep=small]
	\dots && {P_3} && {P_2} && {P_1} && {P_0} && B && 0 \\
	\\
	\dots && {P_3'} && {P_2'} && {P_1'} && {P_0'} && {B'} && 0
	\arrow[from=1-1, to=1-3]
	\arrow["{d_3}", from=1-3, to=1-5]
	\arrow["{f_3}", from=1-3, to=3-3]
	\arrow["{d_2}", from=1-5, to=1-7]
	\arrow["{f_2}", from=1-5, to=3-5]
	\arrow["{d_1}", from=1-7, to=1-9]
	\arrow["{f_1}", from=1-7, to=3-7]
	\arrow[from=1-9, to=1-11]
	\arrow["{f_0}", from=1-9, to=3-9]
	\arrow[from=1-11, to=1-13]
	\arrow["f", from=1-11, to=3-11]
	\arrow[from=3-1, to=3-3]
	\arrow["{d_3'}", from=3-3, to=3-5]
	\arrow["{d_2'}", from=3-5, to=3-7]
	\arrow["{d_1'}", from=3-7, to=3-9]
	\arrow[from=3-9, to=3-11]
	\arrow[from=3-11, to=3-13]
    \end{tikzcd}\]
    Taking tensor with $D$ we have 
    \[\begin{tikzcd}[sep=small]
	\dots && {D \ten_R P_2} && {D \ten_R P_1} && {D \ten_R P_0} && 0 \\
	\\
	\dots && {D \ten_R P_2'} && {D \ten_R P_1'} && {D \ten_R P_0'} && 0
	\arrow[from=1-1, to=1-3]
	\arrow["{d_2}", from=1-3, to=1-5]
	\arrow["{1\ten f_2}", from=1-3, to=3-3]
	\arrow["{d_1}", from=1-5, to=1-7]
	\arrow["{1\ten f_1}", from=1-5, to=3-5]
	\arrow[from=1-7, to=1-9]
	\arrow["{1\ten f_0}", from=1-7, to=3-7]
	\arrow[from=3-1, to=3-3]
	\arrow["{d_2'}", from=3-3, to=3-5]
	\arrow["{d_1'}", from=3-5, to=3-7]
	\arrow[from=3-7, to=3-9]
    \end{tikzcd}\]
    We shall denote the first and second row of complexes as $X^\bullet$ and $Y^\bullet$ respectively. We examine commutativity in the above diagram, where note
    \begin{align*}
        (1\ten d_n) \circ (1\ten d_{n+1}) 
        &= 1\ten (f_n \circ d_{n+1}) \\
        &= 1\ten (d_n\circ f_{n+1}) \\
        &= (1\ten d_n) \circ (1\ten f_{n+1})
    \end{align*}
    Thus we indeed have commutativity. Therefore, this induces maps on the homology group
    \[\f_* :H_n(X^\bullet) \to H_n(Y^\bullet)\]
    where $H_n(X^\bullet)$ is $\tor_n^R(D,B)$ and $H_n(Y^\bullet)$ is $\tor_n^R(D,B')$. This completes the proof.
\end{proof}

\begin{thm}
    Let $0\to A\to B\to C \to 0$ be a SES of left $R$-module and $D$ be a right $R$-module. Then we have a LES (of abelian groups) given by 
    \[\dots \to \tor_2^R(D,C)\to \tor_1^R(D,A) \to \tor_1^R(D,B)\to \tor_1^R(D,C)\]
    \[\to D\ten_R A \to D\ten_R B\to D\ten_R C\to 0\]
\end{thm}
\begin{proof}
    Let $P_\bullet \twoheadrightarrow A$ and $Q_\bullet \twoheadrightarrow C$ be projective resolutions of $A$ and $C$ respectively. By Horseshoe Lemma we have
    \[\begin{tikzcd}[sep=small]
	&& 0 && 0 && 0 && 0 \\
	\\
	\dots && {P_2} && {P_1} && {P_0} && A && 0 \\
	\\
	\dots && {P_2 \oplus Q_2} && {P_1 \oplus Q_1} && {P_0 \oplus Q_0} && B && 0 \\
	\\
	\dots && {Q_2} && {Q_1} && {Q_0} && C & \bullet & 0 \\
	\\
	&& 0 && 0 && 0 && 0
	\arrow[from=1-3, to=3-3]
	\arrow[from=1-5, to=3-5]
	\arrow[from=1-7, to=3-7]
	\arrow[from=1-9, to=3-9]
	\arrow[from=3-1, to=3-3]
	\arrow["{{d_2}}", from=3-3, to=3-5]
	\arrow["{\iota_2}"', hook, from=3-3, to=5-3]
	\arrow["{{d_1}}", from=3-5, to=3-7]
	\arrow["{\iota_1}"', hook, from=3-5, to=5-5]
	\arrow["{{d_0}}", from=3-7, to=3-9]
	\arrow["{\iota_0}"', hook, from=3-7, to=5-7]
	\arrow[from=3-9, to=3-11]
	\arrow[from=3-9, to=5-9]
	\arrow[from=5-1, to=5-3]
	\arrow[from=5-3, to=5-5]
	\arrow["{{\pi_2}}"', two heads, from=5-3, to=7-3]
	\arrow[from=5-5, to=5-7]
	\arrow["{{\pi_1}}"', two heads, from=5-5, to=7-5]
	\arrow[from=5-7, to=5-9]
	\arrow["{{\pi_0}}"', two heads, from=5-7, to=7-7]
	\arrow[from=5-9, to=5-11]
	\arrow[from=5-9, to=7-9]
	\arrow[from=7-1, to=7-3]
	\arrow["{{\delta_2}}"', from=7-3, to=7-5]
	\arrow[from=7-3, to=9-3]
	\arrow["{{\delta_1}}"', from=7-5, to=7-7]
	\arrow[from=7-5, to=9-5]
	\arrow["{{\delta_0}}"', from=7-7, to=7-9]
	\arrow[from=7-7, to=9-7]
	\arrow[from=7-9, to=7-11]
	\arrow[from=7-9, to=9-9]
    \end{tikzcd}\]
    Taking $D\ten_R -$ we have
    \[\begin{tikzcd}[sep=small]
	&& 0 && 0 && 0 \\
	\\
	\dots && {D \ten_R P_2} && {D \ten_R P_1} & 0 & {D \ten_R P_0} && 0 \\
	\\
	\dots && {D \ten_R (P_2 \oplus Q_2)} && {D \ten_R (P_1 \oplus Q_1)} && {D \ten_R (P_0 \oplus Q_0)} && 0 \\
	\\
	\dots && {D \ten_R Q_2} && {D \ten_R Q_1} && {D \ten_R Q_0} && 0 \\
	\\
	&& 0 && 0 && 0
	\arrow[from=1-3, to=3-3]
	\arrow[from=1-5, to=3-5]
	\arrow[from=1-7, to=3-7]
	\arrow[from=3-1, to=3-3]
	\arrow["{1 \ten {d_2}}", from=3-3, to=3-5]
	\arrow["{1 \ten \iota_2}"', from=3-3, to=5-3]
	\arrow["{1 \ten {d_1}}", from=3-5, to=3-7]
	\arrow["{1 \ten \iota_1}"', from=3-5, to=5-5]
	\arrow[from=3-7, to=3-9]
	\arrow["{1 \ten \iota_0}"', from=3-7, to=5-7]
	\arrow[from=5-1, to=5-3]
	\arrow["{1 \ten \gamma_2}", from=5-3, to=5-5]
	\arrow["{1 \ten {\pi_2}}"', from=5-3, to=7-3]
	\arrow["{1 \ten \gamma_1}", from=5-5, to=5-7]
	\arrow["{1 \ten {\pi_1}}"', from=5-5, to=7-5]
	\arrow[from=5-7, to=5-9]
	\arrow["{1 \ten {\pi_0}}"', from=5-7, to=7-7]
	\arrow[from=7-1, to=7-3]
	\arrow["{1 \ten {\delta_2}}"', from=7-3, to=7-5]
	\arrow[from=7-3, to=9-3]
	\arrow["{1 \ten {\delta_1}}"', from=7-5, to=7-7]
	\arrow[from=7-5, to=9-5]
	\arrow[from=7-7, to=7-9]
	\arrow[from=7-7, to=9-7]
    \end{tikzcd}\]
    We shall denote the second, third, fourth row of complexes, which are non-zero, as $X_\bullet, Y_\bullet,$ and $Z_\bullet$, and we claim that the column are SES of complexes.
    
    To see this, we compute a map $1\ten \zeta_0 :D\ten_R(P_0\oplus Q_0)\to D\ten_R P_0$, which is simply the projection to $D\ten_R P_0$. Note
    \[(1\ten\zeta_0)\circ (1\ten \iota_0) = 1\ten (\zeta_0 \circ \iota 0) = 1\ten \id_{P_0} = \id _{D\ten_R P_0}\]
    This implies that $1\ten \iota_0$ must be an injective map. In general $1\ten \iota_\bullet$ is injective. On the other hand, it is clear that $1\ten \pi_\bullet$ is surjective. Thus, we have that the rows of the commutative diagram forms an SES, i.e.
    \[0 \to X_\bullet \to Y_\bullet \to Z_\bullet \to 0\]
    This induces a LES 
    \[\dots \to H_1(X_\bullet) \to H_1(Y_\bullet) \to H_1(Z_\bullet) \to H_0(X_\bullet) \to H_0(Y_\bullet) \to H_0(Z_\bullet) \to 0\]
    where these homology groups are the Tor groups. This completes the proof.
\end{proof}

\begin{pro} [Characterization of flat modules]
    Let $D$ be a right $R$-module. TFAE:
    \begin{enumerate}
        \item $D$ is flat.
        \item $\tor_1^R(D,B)=0$ for all left $R$-module $B$.
        \item $\tor_n^R(D,B)=0$ for all left $R$-module $B$ and $n\geq 1$.
    \end{enumerate}
\end{pro}
\begin{proof}
    \hfill

    $[3. \implies 2.]$ Trivial.

    $[2. \implies 1.]$ Suppose given SES $0\to A \to B \to B \to C \to 0$. By the previous theorem, we have a LES
    \[\dots \to \tor_1^R(D,C)=0 \to D\ten_R A \to D\ten_R B\to D\ten_R C\to 0\]
    This reduces to an SES
    \[0 \to D\ten_R A \to D\ten_R B\to D\ten_R C\to 0\]
    Thus $D$ is flat by definition.

    $[1. \implies 3.]$ Let $P_\bullet \twoheadrightarrow B$ be a projective resolution of $B$. Since $D$ is flat, from the LES
    \[\dots \to P_2 \to P_1 \to P_0 \to B \to 0 \to \dots\]
    it induces another LES
    \[\dots \to D \ten_R P_2 \to D \ten_R P_1 \to D \ten_R P_0 \to 0\]
    where the term $D\ten_R B$ is removed. Since this is a LES, thus all the homology group, i.e. the Tor groups, are trivial. This concludes the proof.
\end{proof}

\begin{re}
    Recall when $R$ is commutative a left $R$-module is equivalent to a right $R$-module. In this case, $\tor_n^R(A,B)\cong \tor_n^R(B,A)$. To prove this it requires the use of double complex, which is not covered here, thus the proof is omitted.

    However, we can check that the statement is true when $n=0$. This is indeed true since 
    \[\tor_0^R(A,B)\cong A\ten_R B \cong B\ten_R A \cong \tor_0^R(B,A)\]
    Here the tensor product is commutative due to commutativity of $R$.
\end{re}

\medskip

\begin{ex}
    It is easy to show that $\tor_n^R(A,\bigoplus B_i) \cong \bigoplus \tor_n^R(A,B_i)$ (this is a tutorial question). We will use this to compute $\tor_n^\Z(A,B)$ where $B$ is a finitely generated $Z$-module. Note
    \[B\cong Z^m \oplus (\Z/d_1\Z) \oplus \dots \oplus(\Z/d_\ell \Z)\]
    And thus
    \[\tor_n^\Z(A,B)\cong \bigoplus_{i=1}^m \tor^\Z_n(A,\Z) \oplus \bigoplus_{i=1}^\ell \tor_n^\Z(A,\Z/d_i\Z)\]
    Note 
    \[\tor_n^Z(A,\Z/d_i\Z)=
    \begin{cases}
        A/d_iA&, n=0\\
        _{d_i}A&, n=1\\
        0&, n\geq 2
    \end{cases}\]
    On the other hand,
    \[\tor_0^\Z(A,\Z)=A\quad \text{ and } \quad \tor_n^\Z(A,\Z)=0\ \forall n\geq 1\]
    Therefore, in this case, $\tor_n^\Z(A,B)$ is fully known.
\end{ex}

\subsection{Group Cohomology}
Recall that $\Z G$ is the set of functions $f$ from $G$ to $\Z$ with finite support. Alternatively, we can think of $\Z G$ as 
\[\sbr{\sum \lambda_g \cdot g:\lambda_g \in \Z\text{ where $\lambda_g$ are almost all zero}}\]
For more details (including its operation), refer to Example \ref{ex: group algebra}. Note also that $\Z G$ is commutative if and only if $G$ is abelian.

\medskip

\begin{defn} [$G$-module]
    Let $G$ be a group (not necessarily abelian) and $A$ be an abelian group. We say $A$ is a $G$-module if there is a group homomorphism $\varphi:G\to \aut{A}$, i.e. $G$ acts on $A$, i.e. $A$ is a $\Z G$-module where $\Z G$ is the group algebra over $\Z$.
\end{defn}

\medskip

\begin{ex}
    \hfill

    \begin{enumerate}
        \item (Trivial $G$-module). $\Z$ is a $G$-module with the trivial $G$-action, i.e. $g\cdot n = n$ for every $g\in G$ and $n\in \Z$. One shall note, however, that this does not mean $\alpha\cdot n = n$ for every $\alpha \in \Z G$, for example
        \[(1+g)\cdot n = 1\cdot n + g\cdot n = n+n = 2n\]
        \item Let $A$ be a $G$-module. The fixed point submodule of $A$ by $G$ is defined to be
        \[A^G = \sbr{a\in A : ga = a \forall g\in G}\leq A\]
        This is a submodule of $A$ where $G$ acts trivially.
        \item Let $V$ be a vector space over field $F$. Then $V$ is $\gl(V)$-module, where recall $\gl(V)$ is just the group fo linear transformation from $V$ to $V$. Furthermore, $V^{\gl(V)}= \sbr{\vec 0}$.
        \item Let $K$ be a Galois extension of $F$ (for example $\Q$). Then $K$ is a $G$-module where $G = \gal(K/F)$. Also $K^G = F$ by the Galois correspondence.
    \end{enumerate}
\end{ex}

\medskip

\begin{lem}
    Let $A$ be a $G$-module. Then $A^G \cong \h_{\Z G}(\Z,A)$ as groups.
\end{lem}
\begin{proof}
    Define $\varphi: A^G \to \h_{\Z G}(\Z, A)$ by $\varphi(a)= \alpha_a$ where $\alpha_a: n \mapsto n\cdot a$ for any $a\in A^G$.

    We first check well-definedness. We check that $\alpha_a \in \h_{\Z G}(\Z,A)$. Since element of $\Z G$ can be expressed as formal sum of $G$, thus it suffices to check that $\alpha_a(g\cdot n) = g\cdot \alpha_a(n)$ 
    \[\alpha_a(g\cdot n) = \alpha_a(n) = na = n(g \cdot a) = g\cdot (na) = g\cdot \alpha_a(n)\]
    Next, we check that $\varphi$ is a group homomorphism. To show $\varphi(a+b)= \varphi(a) + \varphi(b)$, we just have to note that 
    \[\alpha_{a+b}(n) = n(a+b) = na + nb = \alpha_a(n) + \alpha_b(n) = (\alpha_a + \alpha_b)(n)\]
    We now show that $\varphi$ is a group isomorphism by defining its inverse map. Consider $\phi:\h_{\Z G}(\Z, A) \to A^G$ where $\alpha\mapsto \alpha(1)$. It is easy to check that the composition of $\phi$ and $\varphi$ gives identity map, and is thus omitted here.
\end{proof}

\begin{pro}
    Let $F_n := \bigotimes_{i=1}^{n+1} \Z G$ where tensor product is over $\Z$. Then
    \[\dots \to F_n \xto{d_n} F_{n-1} \xto{d_{n-1}} \dots F_1 \xto{d_1} F_0 \xto{\ep} \Z \to 0\]
    is a free resolution of $\Z$ as $\Z G$-module where
    \begin{enumerate}
        \item $F_n$ is $\Z G$-module defined by $g\cdot (g_0 \otimes g_1 \otimes \dots \otimes g_n) := (gg_0) \ten g_1 \ten \dots g_n$.
        \item $F_n$ is a free $\Z G$-module of rank $|G|^n$, i.e. $F_n \cong \bigoplus_{i=1}^{|G|^n} \Z G$ with a free basis
        \[\sbr{1\ten g_1 \dots \ten g_n:g_1, \dots, d_n\in G}\]
        \item $\ep =: d_0:F_0 \to \Z$ is defined by $d_0(g_0)=1$. For $d_1:F_1\to F_0$ where $d_1(g_0\ten g_1)= g_0(g_1-1)$. For $n\geq 2$, we define
        \begin{align*}
            d_n(g_0 \ten g_1 \ten \dots \ten g_n)=
            &(g_0g_1\ten g_2 \ten \dots \ten g_n)\\ 
            &+ \sum_{i=1}^{n-1}(-1)^i(g_0\ten g_1 \ten \dots \ten g_{i-1}\ten g_{i}g_{i+1} \ten \dot \ten g_n)\\ 
            &+ (-1)^n(g_0\ten g_1 \ten \dots \ten g_{n-1})
        \end{align*}
    \end{enumerate}
\end{pro}
\begin{proof}
    The proof is tedious and lengthy, thus it is left as a tutorial question.
\end{proof}

\begin{defn} [Bar resolution / Standard Resolution]
    The free resolution constructed in the previous proposition is called the bar resolution of $\Z$.
\end{defn}

\medskip

\begin{re}
    Historically, instead of writting $(g_0 \ten g_1 \ten \dots \ten g_n)$, it was written as 
    \[(g_0 \mid g_1 \mid \dots \mid g_n)\]
    and this is why it is called bar resolution. We shall adapt this style of writting as well.
\end{re}

\medskip

\begin{defn} [Group cohomology]
    Let $A$ be a $G$-module. The $n$-th group cohomology of $G$ with coefficient set $A$ is defined to be
    \[\ext_{\Z G}^n (\Z, A)\]
    where $\ext_{\Z G}^n (\Z, A)$ is the $n$-th cohomology group of the complex obatined from taking hom on the bar resolution of $\Z$:
    \[0 \to \h_{\Z G}(F_0, A) \xto{d_1^*} \h_{\Z G}(F_1, A) \xto{d_2^8} \h_{\Z G}(F_2, A) \xto{d_3^*}\dots\]
\end{defn}